### 2021-10-14 cv/cv-body.tex
Move preprint to published

\hypertarget{preprints}{%
\section{Preprints}\label{preprints}}

\begin{description}
\tightlist
\item[2021]
English, P., E.J. Ward, C.N. Rooper, R.E. Forrest, L.A. Rogers, K.L.
Hunter, A.M. Edwards, B.M. Connors, \textbf{S.C. Anderson}. Contrasting
climate velocity impacts in warm and cool locations: A meta-analysis
across 38 demersal fish species in the northeast Pacific. EcoEvoRxiv.
\url{https://doi.org/10.32942/osf.io/b87ng}.
\item[2021]
Stockdale, J.E., \textbf{Anderson, S.C.}, Edwards, A.M., Iyaniwura,
S.A., Mulberry, N., Otterstatter, M.C., Janjua, N.Z., Coombs, D.,
Colijn, C., and Irvine, M.A.\ Quantifying transmissibility of COVID-19
and impact of intervention within long-term health care facilities.
medRxiv: 2021.02.01.21249903.
\url{https://doi.org/10.1101/2021.02.01.21249903}.
\end{description}

@@

>>>>

@@

English, P., E.J. Ward, C.N. Rooper, R.E. Forrest, L.A. Rogers, K.L.
Hunter, A.M. Edwards, B.M. Connors, \textbf{S.C. Anderson}. Contrasting
climate velocity impacts in warm and cool locations show that effects of
marine warming are worse in already warmer temperate waters. In press at
Fish and Fisheries. \url{https://doi.org/10.1111/faf.12613}. Open access
preprint: \url{https://doi.org/10.32942/osf.io/b87ng}.
